taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-12-03 paper/manuscript.Rmd
Cleanup

@@

<!--
What other aspects should be included in the table? Citations?
-->

(ref:itis) Integrated Taxonomic Information System [@itis]

@@

Taxonomic indentifiers are a powerful tool for maintaing taxonomic consistency, an essential task for a wide variety of applications. Despite multiple taxonomic standardization efforts, resolving names to taxonomic identifiers is often not a standard step in the research work flow due to difficulty in accessing providers and the time consuming API queries necessary fo resolving even moderately sized data sets. `taxadb` fills an important gap between existing tools and typical research patterns by providing a fast, reproducible approach for matching names to taxonomic identifiers. `taxadb` is not intended as an improvement or replacement for any existing approaches to taxonomic name resolution.In particular, `taxadb` is not a replacement for the APIs or databases provided, but merely an interface to taxonomic naming information contained within that data.

`taxadb` establishes a local database of provider allowing for consistent and reproducible queries. The set of functions operate consistently accross providers returning data in a standardized format.

----

>>>>

<!--

@@

(ref:itis) Integrated Taxonomic Information System [@itis]
-->

@@

Taxonomic indentifiers are a powerful tool for maintaing taxonomic consistency, an essential task for a wide variety of applications. Despite multiple taxonomic standardization efforts, resolving names to taxonomic identifiers is often not a standard step in the research work flow due to difficulty in accessing providers and the time consuming API queries necessary for resolving even moderately sized data sets. `taxadb` fills an important gap between existing tools and typical research patterns by providing a fast, reproducible approach for matching names to taxonomic identifiers. `taxadb` is not intended as an improvement or replacement for any existing approaches to taxonomic name resolution. In particular, `taxadb` is not a replacement for the APIs or databases provided, but merely an interface to taxonomic naming information contained within that data. 
----
